\LARGE \bf Planning with Attitude

### 2020-10-14 paper/main.tex
small tweaks

    \subsection{Satellite Attitude Keep-Out}
        % \todo{Let's add a little more detail here: How about saying the dynamics are \eqref{eq:rigid_body_dynamics} plus a few extra states to capture the bending modes. Also, let's just call the start tracker a camera or sensor.}
        A spacecraft with flexible appendages was tasked to perform a 150 degree slew maneuver while
        ensuring that a body-mounted camera did not point within 40 degrees of a  ``keep-out zone'' around the sun vector. The spacecraft dynamics are presented in detail in~\cite{Tracy2020}, and are based
        on equation \eqref{eq:rigid_body_dynamics} with the addition of six states to account for three flexible modes. Control torques are generated by four reaction wheels.  The slew is motivated by a quadratic cost function that penalizes error from the final attitude, as well as excessive flexible displacement. 
        % \todo{Kevin: add some info on cost function, initial guess (if any), etc.}
        We enforce the camera keep-out zone can with the following constraint,
        \begin{equation}
            \left(\inframe{W}{r_{sun}}\right)^T 
            \left(\toframe{W}{B}{A(q)} \, \inframe{B}{r_{cam}} \right) \leq \cos(40 ^\circ) ,
        \end{equation}
        where $^Br_{cam}$ is the camera line-of-sight unit vector in the body frame and $^Wr_{sun}$ is the unit vector pointing to the sun in the world frame. The attitudes that satisfy this constraint comprise a non-convex set, with the
        constraint itself being nonlinear in $q$.
        \begin{figure}[ht]
            \centering
            \includegraphics{figures/kevins_plots/attitude_slew_plot.tikz}
            \caption{Visualization of the flexible spacecraft slew with a keep-out zone. Attitude is parameterized with a Rodrigues parameter to visualize the trajectory in three dimensions. The constraint surface represents attitudes where the camera line-of-sight is within 40$^\circ$ of the sun. The unconstrained solution violates this constraint, while the constrained solution is able to avoid the keep out zone.}
            \label{fig:keepout}
        \end{figure}

        ALTRO is able to converge on a feasible trajectory for this problem without any initial guess, with the resulting attitude history represented in Fig. \ref{fig:keepout}. Without the camera constraint present, the trajectory will pass through the keep-out
        zone, making the trajectory infeasible. With the keep-out zone constraint present, ALTRO
        is able to generate a trajectory that performs the slew in an efficient manner, while
        keeping the camera sufficiently far from the sun.

        The modifications didn't have a significant impact on runtime performance for this
        example. In our experience, the computational benefits of the proposed methodology are
        problem-dependent, especially for highly nonlinear systems. The following examples result
        in more dynamic and aerobatic behaviors, where the computational benefit of the proposed
        methodology is significant, including an example where the naive method failed to find a
        good solution.

>>>>

    \subsection{Satellite Attitude Keep-Out}
        % \todo{Let's add a little more detail here: How about saying the dynamics are \eqref{eq:rigid_body_dynamics} plus a few extra states to capture the bending modes. Also, let's just call the start tracker a camera or sensor.}
        A spacecraft with flexible appendages was tasked to perform a 150 degree slew maneuver while
        ensuring that a body-mounted camera did not point within 40 degrees of a  ``keep-out zone'' around the sun vector. The spacecraft dynamics are presented in detail in~\cite{Tracy2020}, and are based
        on equation \eqref{eq:rigid_body_dynamics} with the addition of six states to account for three flexible modes. Control torques are generated by four reaction wheels.  A quadratic cost function penalizes error from the desired final attitude as well as displacement of the flexible modes. 
        % \todo{Kevin: add some info on cost function, initial guess (if any), etc.}
        We enforce the camera keep-out zone can with the following constraint,
        \begin{equation}
            \left(\inframe{W}{r_{sun}}\right)^T 
            \left(\toframe{W}{B}{A(q)} \, \inframe{B}{r_{cam}} \right) \leq \cos(40 ^\circ) ,
        \end{equation}
        where $^Br_{cam}$ is the camera line-of-sight unit vector in the body frame and $^Wr_{sun}$ is the unit vector pointing to the sun in the world frame. The attitudes that satisfy this constraint comprise a non-convex set, with the constraint itself being nonlinear in $q$.
        \begin{figure}[ht]
            \centering
            \includegraphics{figures/kevins_plots/attitude_slew_plot.tikz}
            \caption{Visualization of the flexible spacecraft slew with a keep-out zone. Attitude is parameterized with a Rodrigues parameter to visualize the trajectory in three dimensions. The constraint surface represents attitudes where the camera line-of-sight is within 40$^\circ$ of the sun. The unconstrained solution violates this constraint, while the constrained solution is able to avoid the keep out zone.}
            \label{fig:keepout}
        \end{figure}

        ALTRO is able to converge to a locally optimal trajectory for this problem without an initial guess (all controls were initialized to zero). The resulting attitude trajectory is depicted in Fig. \ref{fig:keepout}. Without enforcing the camera constraint, the trajectory passes through the keep-out zone. As noted in Table \ref{tab:timing_results}, the quaternion modifications did not result a significant improvement over the naive implementation of ALTRO for this problem, indicating that the computational benefits are problem dependent. We hypothesize that the more dynamic behaviors in the other examples benefit more from the quaternion modifications than the relatively slow-moving spacecraft.
